\documentclass{article}
\usepackage{marginnote}
\usepackage[top=2cm, bottom=2cm, outer=6cm, inner=2cm, heightrounded, marginparwidth=3cm, marginparsep=1cm]{geometry}
\usepackage{lipsum}
\usepackage{parskip}
\usepackage{amsfonts}
\usepackage{marginfix} % floats sidenots
\usepackage{sidenotes}
\usepackage{amsmath}
\usepackage [english]{babel}
\usepackage [autostyle, english = american]{csquotes}
\MakeOuterQuote{"}
\usepackage{enumitem} % Allows customization of lists
\title{CSC165 Pre-Class Notes Week 1}
\author{Avery Ng}
\date{2024.12.23}



\begin{document}
\maketitle

\section{Mathematical Expression}
\subsection{Sets}

\setlength{\parindent}{0pt}
    

\textbf{Definition 1.1.} \textbf{Sets} are a collection of distinct \textbf{elements} (finite or infinite). 
\begin{itemize}[itemsep=0pt] 
    \renewcommand{\labelitemi}{} % Remove bullet points
    \footnotesize % Reduce text size
    \item The size of a finite set $A$ is denoted by $\lvert A \rvert$.
    \item The \textbf{empty set} is denoted by $\emptyset$.
    \item \textbf{Cardinality} of a set is how many elements
are in the set.$^{1}$
\end{itemize}

\marginnote{\footnotesize $^{1}$ It is important to note that the hierarchy of cardinalities is
$\#\mathbb{N} = \#\mathbb{Z} = \#\mathbb{Q} < \#\mathbb{R} = \#\mathbb{C}$.} 

\textbf{Examples} \\
\emph{Finite sets } \hfill $\{a, b, c, d\}$, $\{2, 4, 10, 11\}$ \\
Set of tuples \hfill $\{(Ava Doe, \$ 700, 50), (Donald,\$ 670, 30)\}$ \\
\emph{Infinite sets} \\
$ \mathbb{R} $  = real numbers \\
$ \mathbb{Q} $ = rational numbers \\
$ \mathbb{Z}$ = integers : $ \{\ldots, 2, -1, 0, 1, 2, \ldots\} $ \\
$ \mathbb{Z}^{+} $ = positive integers : $ \{1, 2, \ldots\} $ \\
$ \mathbb{N} $ = all natural numbers : $\{ 0, 1, 2, \ldots \} $ = $ \mathbb{Z}^{+} $  $\cap$ {$\emptyset$}\\

\marginnote{\footnotesize $^2$ Some definitions on binary operators and relations: \\
$=$ \hfill equals \\
$\in$ \hfill in \\ 
$\notin$ \hfill not in\\
$\subseteq$ \hfill subset \\
$\cap$ \hfill intersection \\
$\cup$ \hfill union \\ 
$\setminus$ \hfill set difference \\ 
$\times$ \hfill Cartesian product \\
$\mathcal{P}(\mathbb{A})$ \hfill power set}


A string of length 0 is called the \emph{empty string} and is denoted 
by $\epsilon$.

A set of all natural numbers greater or equal to five can be denoted by:
$$ \{ x \mid x \in \mathbb{N} \text{ and } x \geq 5 \} $$ 
(left side: description, right side: condition)

The set of all rational numbers can be denoted by $^2$
$$ \mathbb{Q} = \left\{ \frac{p}{q} \; \middle\vert \; p, q \in \mathbb{Z} \; and \; q \neq 0 \right\} $$


\subsubsection*{Operations on sets}
The size of a set, $\mid \emph{A} \mid$, is an example of a set operation. There
are many other common set operations.$^3$

\marginnote{$^3$ Cartesian products are all \emph{pairs} $(a, b)$ where $a$ and $b$ are
elements of their respective sets.}

\textbf{Examples}\\
\emph{Returns booleans} \hfill \emph{Returns sets}\\
element of A: $x \in A$, $y \not\in A$ \hfill union: $A \cap B$, intersection: $A \cup B$ \\
subset of: $A \subseteq B$ \hfill difference of A and B:  $A \setminus B$ 
$\{ x \mid x \in A \text{ and } x \notin B \}$ \\
contains same elements: $A = B$ \hfill Cartesian product: $A \times B$, power set of A: $\mathcal{P}(\mathbb{A})$ \\ 

Power sets are sets containing \emph{all} subsets of $A$. If $A = {1, 2, 3}$, then
$$\mathcal{P}(\mathbb{A}) = \{\emptyset, \{1\}, \{2\}, \{3\}, \{1, 2\}, 
\{1, 3\}, \{2, 3\}, \{1, 2, 3\}\}$$

% 1.2 Functions
\newpage
\subsection{Functions}
\textbf{Definition 1.2.} Let $A$ and $B$ be sets. A \textbf{function} $ f
: A \to B $ is a mapping from elements in $A$ to elements in $B$. 
\begin{itemize}[itemsep=0pt] 
    \renewcommand{\labelitemi}{} % Remove bullet points
    \footnotesize % Reduce text size
    \item $A$ is the \textbf{domain} of the function.
    \item $B$ is the \textbf{codomain} of the function.
    \item $Range$ of \emph{f} is the set containing all possible outputs \{$ f(x)| x \in A $\}
\end{itemize}


\textbf{Example} \\
Predecessor function \hfill $Pred: \mathbb{Z} \to \mathbb{Z} $ 
\begin{itemize}[itemsep=0pt] 
    \renewcommand{\labelitemi}{} % Remove bullet points
    \footnotesize % Reduce text size
    \item Given $Pred(x) = x - 1$: $Pred(A) = \{ \ldots, (-2, -3), (-1, -2), (0, -1), (1, 0), (2, 1), \ldots \} $ 
\end{itemize}
Arity function: k-ary function$^4$ \hfill $f : A_1 \times A_2 \times \ldots \times A_k \to B$ 
\marginnote{$^4$ k-ary refers to terms like unary, binary, ternary functions
that take one, two, and three inputs respectively.}
\begin{itemize}[itemsep=0pt] 
    \renewcommand{\labelitemi}{} % Remove bullet points
    \footnotesize % Reduce text size
    \item Addition operator (binary) takes 2 real numbers and return sum \hfill $ + : \mathbb{R} \times \mathbb{R} \to \mathbb{R} $ 
\end{itemize}
Predicate function (codomain is True and False) \hfill $ f : \mathbb{N} \to $ \{True, False\}
\begin{itemize}[itemsep=0pt] 
    \renewcommand{\labelitemi}{} % Remove bullet points
    \footnotesize % Reduce text size
    \item Given \emph{any} predicate $P: A \to \{T, F\}$, construct a \emph{specific} subset $S_P \subseteq A$ 
        as follows: \[ S_P = \{x \in A \mid P(x) = T\}. \]
    Given \emph{any} subset $S \subseteq A$, construct a \emph{specific} predicate $P_S: A \to \{T, F\}$ as follows: \[
    P_S(x) =
        \begin{cases}
            T, & \text{if } x \in S, \\
            F, & \text{if } x \notin S.
        \end{cases} \]
    \item Predicates and sets are closely related.
    \begin{itemize}[itemsep=0pt] 
        \renewcommand{\labelitemi}{} % Remove bullet points
        \footnotesize % Reduce text size
        \item[] Set \hfill Predicate \\
        $\{ x \mid x \in A \; and \:P(x) = True\}$. \hfill $ P : A \to$ \{True, False\} \\
        $B \subseteq A$ \hfill $P : A \to $ \{True, False\} by $P(x) = $ True if $x \in A$ \\
        \{0, 2, 4, \ldots \} \hfill  $ Even : \mathbb{N} \to $ \{True, False\}
    \end{itemize}

\end{itemize}


% 1.3 Summation and product notation
\subsection{Summation and product notation}
\textbf{Definition 1.3.} The \textbf{summation notation} is used to express
sums of terms where each term follows a pattern.
$$ \sum_{i=1}^{100} \frac{i + i^2}{3 + i} $$
$i$ is the \emph{index of summation}, 1 and 100 are the \emph{lower} and 
\emph{upper bounds} of the summation.
\[
\sum_{i=j}^{k} f(i) = f(j) + f(j+1) + f(j+2) + \dots + f(k).
\]

\textbf{Definition 1.4.} The \textbf{product notation} is similar to the 
summation notation, but is used to abbreviate multiplication instead.
$$ \prod_{i=j}^{100} f(i) = f(j) \times f(j+1) \times \ldots \times f(k) $$

\marginnote{$^5$ These values are chosen so that the overall value of the 
expression is not changed when adding an empty summation or multiplying
by an empty product.}
The lower bound can be greater than its upper bound, in which case it
is an \emph{empty} summation or product$^5$ 
\begin{itemize}
    \item Summations have a sum of 0: When \(j > k\), \(\sum_{i=j}^{k} f(i) = 0.\)
    \item Products have a product of 1: When \(j > k\), \(\prod_{i=j}^{k} f(i) = 1.\)
\end{itemize}


\section*{Theorem 1.1}

For all \(n \in \mathbb{N}\), the following formulas hold:

\begin{enumerate}
    \item For all \(c \in \mathbb{R}\), \(\sum_{i=1}^n c = c \cdot n\) (sum with constant terms).
    \item \(\sum_{i=1}^n i = \frac{n(n+1)}{2}\) (sum of consecutive numbers).
    \item \(\sum_{i=1}^n i^2 = \frac{n(n+1)(2n+1)}{6}\) (sum of consecutive squares).
    \item For all \(r \in \mathbb{R}\), if \(r \neq 1\), then \(\sum_{i=0}^{n-1} r^i = \frac{r^n-1}{r-1}\) (sum of powers).
    \item For all \(r \in \mathbb{R}\), if \(r \neq 1\), then \(\sum_{i=0}^{n-1} i \cdot r^i = \frac{nr^n}{r-1} - \frac{r(r^n-1)}{(r-1)^2}\) (arithmetico-geometric series).
\end{enumerate}

\section*{Theorem 1.2}

\[
\sum_{i=m}^n (a_i + b_i) = \left( \sum_{i=m}^n a_i \right) + \left( \sum_{i=m}^n b_i \right) \quad \text{(separating sums)}
\]

\[
\prod_{i=m}^n (a_i \cdot b_i) = \left( \prod_{i=m}^n a_i \right) \cdot \left( \prod_{i=m}^n b_i \right) \quad \text{(separating products)}
\]

\[
\sum_{i=m}^n c \cdot a_i = c \cdot \left( \sum_{i=m}^n a_i \right) \quad \text{(factoring out constants, sums)}
\]

\[
\prod_{i=m}^n c \cdot a_i = c^{n-m+1} \cdot \left( \prod_{i=m}^n a_i \right) \quad \text{(factoring out constants, products)}
\]

\[
\sum_{i=m}^n a_i = \sum_{i'=0}^{n-m} a_{i'+m} \quad \text{(change of index \(i' = i-m\))}
\]

\[
\prod_{i=m}^n a_i = \prod_{i'=0}^{n-m} a_{i'+m} \quad \text{(change of index \(i' = i-m\))}
\]

\marginnote{$^6$ For all non-negative real numbers $a$ and $b$, and
all strictly increasing functions $f : \mathbb{R}^{\geq 0} \to \mathbb{R}^{\geq 0}$,
if $a \leq b$, then $f(a) \leq f(b) $. This also follows the strict equality substitution: \\
if $a < b$, then $f(a) < f(b)$. }
% 1.4 Inequalities
\subsection{Inequalities}

\section*{Theorem 1.3} For all real numbers $a$, $b$, and $c$, the following are true:$^{6}$
\begin{enumerate}[label=(\alph*)]
    \item If $a \leq b$ and $b \leq c$, then $a \leq c$.
    \item If $a \leq b$, then $a + c \leq b + c$.
    \item If $a \leq b$ and $c > 0$, then $ac \leq bc$.
    \item If $a \leq b$ and $c < 0$, then $ac \geq bc$.
    \item If $0 < a \leq b$, then $\frac{1}{a} \geq \frac{1}{b}$.
    \item If $a \leq b < 0 $, then $\frac{1}{a} \geq \frac{1}{b}$.
\end{enumerate}

If any of the above equalities are replaced with a strict equality, then the 
corresponding "then" equality will also be strict.$^7$
\marginnote{$^7$ A strict equality is expressed by $>$ or $<$.}

The implications of the inequalities is that adding or multipying by positive
numbers preserves inequalities, while multiplying by negative numbers or
taking reciprocals reverses inequalities. 


% 1.5 Propositional logic 
\subsection{Propositional logic}
\textbf{Definition 1.5.} A \textbf{proposition} is a statement that is either
True or False.

\textbf{Examples} 
\begin{itemize}
    \item $ 2 + 1 = 3$
    \item $ 4 + 3 < 8$
    \item Every even number greater than 2 is the sum of two prime numbers
    \item Python's \verb|list.sort| is correct on every input list
    
\end{itemize}
\begin{itemize}[itemsep=0pt] 
    \renewcommand{\labelitemi}{} % Remove bullet points
    \footnotesize % Reduce text size
    \item \textbf{Propositional variables} are used to represent propositions. The variable
    names start at \emph{p} by convention.  
    \item \textbf{propositional/logical operator} is a predicate whose arguments 
    must be either True or False.
    \item \textbf{propositional formula} is an expression built up from propositional
    variables by applying the following operators.
\end{itemize}

\subsubsection*{Basic operators}
\marginnote{$^{8}$ There are two different \emph{or's}, the \emph{exclusive} and
the \emph{inclusive}. Exclusive is having one but not the other, inclusive
is having either or both. Usually, the inclusive \emph{or} is used. The exclusive
\emph{or} is denoted by $\oplus$.}
\begin{tabular}{|p{2cm} p{1cm} p{1cm} p{7cm}|}
    \textit{Negation} & \textbf{NOT} & $\neg$ & Unary negation operator that flips the truth value. \\
    \textit{Conjunction} & \textbf{AND} & $\land$ & Binary conjunction operator that returns True when both
    arguments are True. \\
    \textit{Disjunction} & \textbf{OR} & $\lor$ & Binary disjunction operator that returns True when at least
    one argument is True. \\
\end{tabular}

These are some common operators on propositional variables.$^{8}$ 

\subsubsection*{Implication operator}
\textbf{Definition 1.6.} The \textbf{implication} $p \implies q $ asserts 
that whenever $p$ is True, $q$ must be True. 
\begin{itemize}[itemsep=0pt] 
    \renewcommand{\labelitemi}{} % Remove bullet points
    \footnotesize % Reduce text size
    \item The statement $p$ is called the \textbf{hypothesis} of the implication.
    \item The statement $q$ is called the \textbf{conclusion} of the implication.
    \item The \textbf{converse} of an implication switches
    the hypothesis and conclusion. The converse of $p \implies q$ is $q \implies p$.
    These two equations are not logically equivalent.
\end{itemize}



\begin{center}
    
\begin{tabular}{|p{1cm} p{1cm} p{1cm}|}
    \hline
    $p$ & $q$ & $p \Rightarrow q$ \\
    \hline 
    False & False & True \\
    False & True & True \\
    True & False & False \\
    True & True & True \\
    \hline   
\end{tabular}
\end{center}



The two cases where $ p \implies q$ is True even though $p$ is False are
called \textbf{vacuous truth} cases. These are True because the statement
does not say anything about the behaviour of $q$ (conclusion) when $p$ (hypothesis) is False. 
If the premise $p$ doesn't occur, the "promise" doesn't need to be upheld. The conclusion  
$q$ becomes irrelevant, so the statement is considered true. When $p$ is False, 
$ p \implies q$ is always true because the condition under which it would be False 
(True premise with a False conclusion) never arises.


The following two formulas are equivalent to $p \implies q$:

$\neg p \lor q$ \hfill This uses the vacuous truth cases. \\
$\neg q \Rightarrow \neg p$ \hfill This is the \textbf{contrapositive} case.

\textbf{Example$^{9}$} \\
If $p \implies q$ is \hfill "If it rains, then the ground will be wet." \\
$\neg p \lor q$ would be \hfill "It is not raining or the ground is wet." \\
$\neg q \implies \neg p$ would be \hfill "It is not raining, then the ground is not wet."



\subsubsection*{Biconditional operator}
\marginnote{
\begin{tabular}{|p{0.8cm} p{0.8cm} p{1.5cm}|}
    \hline
    $p$ & $q$ & $p \iff q$ \\
    \hline 
    False & False & True \\
    False & True & False \\
    True & False & False \\
    True & True & True \\ 
    \hline   
\end{tabular}
}
\textbf{Definition 1.7.} The \textbf{biconditional} operator denoted by $p \iff q$ 
returns True when both $p \implies q$ and $q \implies p$ are True. In other words,
$p \iff q$ abbreviates $(p \Rightarrow q) \land (q \Rightarrow p)$.

This condition can be phrased any of the below: 
\begin{center}
"If $p$ then $q$, and if $q$ then $p$." \\
"$p$ if and only if $q$." \\
"$p$ if $q$."
\end{center}

\textbf{Definition 1.8.} A \textbf{tautology} is a formula that is always
True for every possible assignment of values to its propositional variables. E.g. 
$(p \Rightarrow q) \Leftrightarrow (\neg p \lor q)$, $(\neg(p\lor q)) 
\Leftrightarrow (\neg p \land \neg q)$.



% 1.6 Predicate logic 
\subsection{Predicate logic}
\marginnote{$^{9}$ Examples of predicates: 
the operators = and $<$ both return True or False based on operands}
\textbf{Predicates}, we know they have a codomain of True or False. 
We can extend this definition to be "A statement whose truth depends on one or
more variables from any set."$^9$

When we substitute values into a predicate, we obtain a proposition:
$P(x, y) $ is the statement $x^2 = y$ \hfill $P(5, 25)$ is True, $P(5, 24)$ is False.

We can complete the definiton of the above statements by giving the domain
of the prediate. In fact, \textbf{it is not a predicate if we do not give the domain.}

\begin{center}
$ P(x) : $ "$x$ is a power of 2," \quad where x$ \in \mathbb{N} $
\end{center}

\subsubsection*{Quantification of variables}
Truth aggregation is when we want to express a predicate's truth values for
all elements of its domain, like the inequality $x^2 - 2x + 1 > 0$. 

There are two ways we can express this truth aggregation using quantifiers, 
which modify predicates by specifying how a variable should be interpreted.

\marginnote{$^{10}$ These examples are stating that there must be \emph{at least}
one of the variable that satisfies the condition --- a continuous OR operation.}
\textbf{Definition 1.9.} The \textbf{existential quantifier}, $\exists$, 
abbreviates "there exists an element in the domain that satisfies the
given predicate." 


\textbf{Examples$^{10}$}
\begin{center}
\begin{tabular}{|c p{7.54cm}|}
    $\exists x \in \mathbb{N}$, $x \geq 0$ & There exists a natural number
    $x$ that is greater than or equal to zero. \\
    $\exists y \in \mathbb{N}$, $y = 2^a$  & There exists a natural number 
    $y$ that is a power of 2.
\end{tabular}
\end{center}

\textbf{Definition 1.10.} The \textbf{universal quantifier}, $\forall$,
abbreviates "\emph{every} element in the domain satisfies the given predicate."

\marginnote{$^{11}$ In contrast to the above, this asks for \emph{all} 
elements to meet the condition, like a continuous AND operation.}
\textbf{Examples$^{11}$}
\begin{center}
\begin{tabular}{|c p{7.54cm}|}
    $\forall x \in \mathbb{N}$, $x \geq 0$ & Every natural number is
    $x$ that is greater than or equal to zero. \\
    $\forall y \in \mathbb{N}$, $y = 2^a$  & Every natural number is  
    $y$ that is a power of 2.
\end{tabular}
\end{center}

\subsubsection*{Understanding multiple quantifiers}
It is important to note that the ordering of quantifiers \emph{do} matter in
some cases.

For commutative operators like addition and multiplication, order does not
matter. The universal operator is commutative if used consecutively:
$$\forall x \in S_1, \forall y \in S_2, P(x, y)$$
$$\forall y \in S_2, \forall x \in S_1, P(x, y)$$
These formulas are equivalent. In fact, we can combine these quantifications
since the variables have the same range!
$$\forall x, y \in S, P(x, y)$$
This reads, "every $x$ and $y$ in $S$ follows $P(x, y)$."

The same follows for consecutive existential quantifiers:
$$\exists x \in S_1, \exists y \in S_2, P(x, y) \quad \quad 
\exists y \in S_2, \exists x \in S_1, P(x, y)$$
This can be summed up as $\exists x, y \in S, P(x, y)$, read as 
"there is at least one pair of elements $x$ and $y$ that satisfy $P(x,y)$."

This is \emph{not} the case for alternating quantifiers however.

\textbf{Example}
$$\forall a \in A, \exists b \in B, Likes(a, b)$$
"For every person $a$ in $A$, there exists a person $b$ in $B$, that $a$ likes $b$."
$$\exists b \in B, \forall a \in A, Likes(a, b)$$
"There exists a person $b$ in $B$, where for every person $a$ in $A$, $a$ likes $b$"

In both these cases, the first variable is \emph{independent} of the
second variable. Read nested quantifiers from left to right!

\subsubsection*{Sentences in predicate logic}
With quantifiers, propositional operators, and predicates, we can represent 
statements using \textbf{sentences}.

\marginnote{$^{12}$ Sometimes a quantified variable will be refered to as 
a \textbf{bound} variable, and an unquantified variable a \textbf{free} 
variable.}
\textbf{Definiton 1.11.} A \textbf{sentence} is a formula with no unquantified 
\newline variable.$^{12}$ This ensures that the formula has a fixed truth value.

\textbf{Examples} \\
$\forall x \in \mathbb{N}, x^2 > y$ \hfill Not a sentence since $y$ is not bound. \\
$\forall x, y \in \mathbb{N}, x^2 > y$ \hfill Is a sentence since both variables are bound. 

\subsubsection*{Manupulating negation}
For any formula, we can state its negation by preceding it by a $\neg$ symbol.

$\forall x \in \mathbb{N}, x \geq 0$ \hfill  $\neg(\forall x \in \mathbb{N}, x \geq 0)$

\marginnote{$^{13}$ Note that many of these rules lead into switching from 
\textit{and} to \textit{or}, and $\forall$ to $\exists$, and vice versa. Try 
not to memorize these, but to understand them.}
Though, sometimes it is hard to transliterate the formula. Instead, there are 
\textit{simplification rules}$^{13}$

$\neg(\neg p)$ \hfill p \\
$\neg(p \lor q)$ \hfill $(\neg p) \land \neg(q)$ \\
$\neg(p \land q)$ \hfill $(\neg p) \lor (\neg q)$ \\
$\neg(p \Rightarrow q)$ \hfill $p \land (\neg q) ^{14}$ \\
$\neg(p \Leftrightarrow q)$ \hfill $(p \land (\neg q)) \lor ((\neg p)\land q)$ \\
$\neg(\exists x \in S, P(x))$ \hfill $\forall x \in S, \neg P(x)$ \\
$\neg(\forall x \in S, P(x))$ \hfill $\exists x \in S, \neg P(x)$ 

\marginnote{$^{14}$ As a reminder, $p \Rightarrow q$ is equivalent to 
$ p \land \neg q$.} 

\subsubsection*{Avoid commas}
Commas can cause ambiguity when connecting propositions.
$$P(x), Q(x)$$
Does this mean $P(x)$ \textit{and} $Q(x)$? Or $P(x)$ \textit{then} $Q(x)$? 

We must never use commas to \textbf{connect propositions}.

Commas have two valid uses only:
\begin{itemize}
    \item Immediately after variable quantification, or separating two variables 
        with the same quantification
    \item Separating arguments to a predicate
\end{itemize}

\textbf{Example} 
$$\forall x, y \in \mathbb{N}, \forall x \in \mathbb{R}, P(x, y) \Rightarrow Q(x, y, z)$$

\subsubsection*{Defining predicates}
\textbf{Definiton 1.12.} Let $n, d \in \mathbb{Z}$. We want to say that $d$ 
divides $n$, or $n$ is divisible by $d$, when there exists a $k \in \mathbb{Z}$ 
such that $n = dk$. So, we will use the notation $d \mid n$ to represent 
"$d$ divides $n$." This is a \textit{binary} \textbf{divisibility predicate}. 

\textbf{Examples} \\
Let us express the statement "For every integer $x$, if $x$ divides 10, then 
it also divides 100" with the divisibility predicate, and without.

\textbf{Without the predicate}:
$$\forall x \in \mathbb{Z}, (\exists k \in \mathbb{Z}, 10 = kx) \Rightarrow 
(\exists k \in \mathbb{Z}, 100 = kx)$$
\marginnote{$^{15}$ Note that there are two different $k$ variables, we could 
also express this using $k_1$ and $k_2$.}
"For every integer $x$, if there exists an integer $k$ such that $kx = 10$, then 
for another integer $k$, $kx = 100$."$^{15}$

\textbf{With the predicate}:
$$\forall x \in \mathbb{Z}, x \mid 10 \Rightarrow x \mid 100$$ 
Much easier, isn't it? 

We can use this definiton to formally define prime numbers.

\textbf{Definition 1.13.} Let $p \in \mathbb{N}$. A \textbf{prime} number is greater 
than 1, and the only natural numbers that divide it are 1 and itself. Primes are
restricted to being positive. 

\textbf{Example} \\
Let $Prime(p)$ denote that "$p$ is a prime number."
$$Prime(p) : p > 1 \land (\forall d \in \mathbb{N}, d \mid p \Rightarrow 
d = 1 \lor d = p), \quad p \in \mathbb{N}$$
Let us express the property that "there are infinitely many primes." \\
How do we express \textit{infinitely many}? Since we know that $ \mathbb{N}$ is
infinite, we can express the statement as "every natural number has a prime 
number larger than it."
$$\forall n \in \mathbb{N}, \exists p \in \mathbb{N}, p > n \land Prime(p)$$

\marginnote{$^{16}$ First conjectured by Pierre de Fermat in 1637, he states that 
the margins of the text \textit{Arithmetica} were too narrow to fit his proof!}
\textbf{Definition 1.14.} \textbf{Fermat's Last Theorem} states that there are 
no three positive integers $a$ , $b$, and $c$ that satisfy $a^n + b^n = c^n$ for 
any integer $n > 2$.$^{16}$

Let us express this theorem using predicate logic. 

Which of these variables are quantified? $n$ is certainly bound to the range of 
for all $n > 2$ and $n$ being an integer. $a$, $b$, and $c$ are not specifically 
bound, but since the theorm states \textit{None} of them satisfy the statement, 
we can say "there does not exist" instead.
$$\forall n \in \mathbb{N}, n > 2 \Rightarrow \neg (\exists a, b, c \in 
\mathbb{Z}^+, a^n + b^n = c^n )$$
Following negation rules, we can push this negative inwards closer to the predicates.
$$\forall n \in \mathbb{N}, n > 2 \Rightarrow (\exists a, b, c \in 
\mathbb{Z}^+, a^n + b^n \ne c^n)$$

\subsubsection*{Formula conventions}
Operation precedence in decreasing order:
\begin{center}
\begin{enumerate}
    \item $\neg$
    \item $\lor, \land$
    \item $\Rightarrow, \Leftarrow$
    \item $\forall, \exists$
\end{enumerate}
\end{center}
Combinations of operations at the same level \textit{must} be disambiguated 
using parentheses. 

The $\lor$ and $\land$ operators are \textit{associative}, meaning that their 
orders do not matter. But the implicator operator is \textit{not associative}. 

Variable naming conventions state that variables should have distinct names 
within the same formula.
$$(\forall x \in \mathbb{N}, f(x) \geq 5) \lor (\exists x \in \mathbb{N}, f(x) < 5)$$
Although the above is correct since variables only exist in the scope of their 
parentheses, we still prefer to use the following:
$$(\forall x \in \mathbb{N}, f(x) \geq 5) \lor (\exists y \in \mathbb{N}, f(y) < 5)$$

\end{document}